{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2025-02-23 Notebook LaTEX/R-WAPG/paper3.tex
>w<, fix cringe shit

            The numerical experiment shows that FR-WAPG initially behaves similar to M-FISTA, but as the iteration goes on, it started to behave like V-FISTA. 
            Unfortunately it's numerically verified that the method is not monotone in general, and it just looks monotone on the graph. 

@@

            Figure \ref{fig:simple-quadratic-r-wapg-mu-estimates} showcases the results. 
            It shows that, the values oscillate and converges to the true $\mu$ value. 

@@

            The problem of LASSO has smooth, nonsmooth additive parts given by: 

@@

            A random matrix $A$ is realized and is fixed and the for all test algorithms and all repetitions. 

@@

            The results are showcased in Figure \ref{fig:batched-lasso}. 

@@

            Another quantity of interest is the estimates of $\mu$ on each iteration of the algorithm. 
            A single experiment were conducted and the estimates and $\delta_k$ are in Figure \ref{fig:single-lass-mu-estimates}

@@

            One of the most important feature is that the estimate $\mu$ doesn't converge to the true value, but it didn't affect the convergence of $\delta_k$.

\section{Discussions}
    This paper provides the results of an upper bound (Proposition \ref{prop:wapg-convergence}) on the optimality gap $F(x_k) - F^*$ for smooth plus nonsmooth composite optimization problem with convex objectives where under the much weaker assumption for the momentum parameter specified by Definition \ref{def:rwapg-seq}. 
    The proposed R-WAPG unifies the convergence proof for major Euclidean variants of FISTA with strong convexity parameter $\mu \ge 0$. 
    To the best of our knowledge, there is no framework had been identified yet in the literatures that proves the convergences of several variants (with and without strong convexity parameter) with momentum sequences that doesn't follow the Nesterov's rule. 
    \par
    In addition, we proposed explorative numerical experiments for Free R-WAPG (Algorithm \ref{alg:free-rwapg}) showcasing a parameter free algorithm that doesn't use the idea of restarting to achieve competitive convergence rate. 
    Unfortunately a precise description of the convergence rate of Free R-WAPG remains a mystery. 
    Our convergence framework gives an upper bound using the sequence $(\alpha_k)_{k \ge 0} \in (\mu/L, 1)$, but it requires knowing what the sequence would be in advanced given the initial conditions and the objective function. 
    \par
    From a practical perspective, Algorithm \ref{alg:free-rwapg} shows competitive results of convergence of strongly convex function.  
    The algorithm behaves in way having characteristics of both V-FISTA and M-FISTA which is fascinating. 
    In addition, of being parameter free, the algorithm works well with auto-differentiation framework because it requires the function value at the same point where the gradient is evaluated at $y_k$. 
    We do note that in the case when function is not strongly convex, the function value converges without $\Vert \mathcal G_L(y_k)\Vert$ converging.

>>>>

            This numerical experiment shows that FR-WAPG initially behaves similar to M-FISTA, but it then started to behave like V-FISTA. 
            It's numerically verified that the method is not monotone in general, and it just looks monotone in this experiment on this plot. 

@@

            Figure \ref{fig:simple-quadratic-r-wapg-mu-estimates} shows the estimated $\mu_k$ of FR-WAPG on the left and the convergence rate of the test algorithms on the right for one specifice initial condition. 
            It shows the values of $\mu_k$ oscillates and converges to the true value of $\mu$. 
            Observe that the initial fast descent slows and FR-WAPG diverges from M-FISTA as $\mu_k$ converged. 

@@

            The problem of LASSO has smooth and nonsmooth additive parts given by: 

@@

            A random matrix $A$ is realized and is fixed for all test algorithms and all repetitions. 

@@

            Figure \ref{fig:batched-lasso} shows the results of the two experiments.

@@

            The experiment results shows faster convergence rate of FR-WAPG relative to V-FISTA, and it also shows that it behaves similarly to M-FISTA. 
            In addition, an experiment were conducted to show the estimate $\mu_k$ and optimality gaph $F(x_k) - F^*$ in Figure \ref{fig:single-lass-mu-estimates}. 

@@

            Make the important observation that $\mu_k$ didn't converge to the true value in this case, however it didn't affect the convergence of $F(x_k) - F^*$.

\section{Discussions}
    This paper provides the results of an upper bound on the optimality gap $F(x_k) - F^*$ for smooth plus nonsmooth composite optimization problem with convex objectives where under the much weaker assumption for the momentum parameter specified by Definition \ref{def:rwapg-seq}. 
    The proposed R-WAPG unifies the convergence proof for major Euclidean variants of FISTA with strong convexity parameter $\mu \ge 0$. 
    To the best of our knowledge, there is no framework had been identified yet in the literatures that proves the convergences of several variants (with and without strong convexity parameter) with momentum sequences that doesn't follow the Nesterov's rule. 
    \par
    In addition, we proposed explorative numerical experiments for Free R-WAPG (Algorithm \ref{alg:free-rwapg}) showcasing a parameter free algorithm that doesn't use the idea of restarting to achieve competitive convergence rate. 
    Unfortunately a precise description of the convergence rate of Free R-WAPG remains a mystery. 
    Our convergence framework gives an upper bound using the sequence $(\alpha_k)_{k \ge 0} \in (\mu/L, 1)$, but it requires knowing what the sequence would be in advanced given the initial conditions and the objective function. 
    \par
    From a practical perspective, Algorithm \ref{alg:free-rwapg} shows competitive results of convergence of strongly convex function.  
    The algorithm behaves in way having characteristics of both V-FISTA and M-FISTA which is fascinating. 
    In addition, of being parameter free, the algorithm works well with auto-differentiation framework because it requires the function value at the same point where the gradient is evaluated at $y_k$. 
    We do note that in the case when function is not strongly convex, the function value converges without $\Vert \mathcal G_L(y_k)\Vert$ converging.
